Scaling up the hyperparameter grid for Naomi

### 2023-07-13 src/dev_scale-grid/scale-grid.Rmd
Rename Rs as Cs (stands for "covariance scaled") #58

Rs <- diag(1 / sqrt(df_std$mean_var)) %*% C %*% diag(1 / sqrt(df_std$mean_var))
plot_matrix(Rs)

eigenRs <- eigen(Rs)
plot_total_variation(eigenRs, label_x = 5)

rownames(eigenRs$vectors) <- hypers
plot_pc_loadings(eigenRs)
```

>>>>

Cs <- diag(1 / sqrt(df_std$mean_var)) %*% C %*% diag(1 / sqrt(df_std$mean_var))
plot_matrix(Cs)

eigenCs <- eigen(Cs)
plot_total_variation(eigenCs, label_x = 5)

rownames(eigenCs$vectors) <- hypers
plot_pc_loadings(eigenCs)
```
